Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-06-03 main.tex
Update on Overleaf.

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

>>>>

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. {\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (, eV) and H$_2^+$ destruction (,eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.
